
\begin{abstract}

This paper examines how family structure affects educational outcomes when unexpected shocks dramatically increase parental time requirements for children's learning. Using administrative and survey data from Peru, I employ a difference-in-differences strategy that compares children with siblings to only children before, during, and after school closures caused by Covid-19. Students with siblings experienced significantly larger learning losses of up to 0.06 standard deviations in GPA and 0.17 standard deviations in standardized exams, with effects intensifying as the number of siblings increased. These differential impacts persist after schools reopened and appear across diverse subpopulations. Evidence points to parental time constraints as the primary mechanism. Effects are largest during primary education when parental investment matters the most and in families with higher socio-economic resources who tend to spend more time with their children. Additionally, using school enrollment age cutoffs, I show that having a younger sibling at home rather than in school significantly reduces older siblings' academic performance and parental time invested in them. Consistent with these results, parents of students with siblings also reduced their expectations that their children will achieve higher education by 3.2 pp. Overall, these findings reveal fundamental insights about family resource allocation under stress. When external education support disappears, the dilution of parental time across multiple children creates substantial disadvantages for larger families. %This has important implications for understanding how families adapt to crises and why larger families may be systematically vulnerable when parental time suddenly becomes the critical input in education production.
%became more pessimistic about their children's educational prospects.
\\
\textit{JEL Codes: I21, I24, D13}
\end{abstract}

%   I2 Education and Research Institutions
    % 	I20 	General 
    %   I21 	Analysis of Education
    %	I23 	Higher Education • Research Institutions
    %	I24 	Education and Inequality
    %	I26 	Returns to Education 
    %   I28 	Government Policy     
    
%   D1 	Household Behavior and Family Economics 
    % 	D13 	Household Production and Intrahousehold Allocation 
    %   D19  other

%   J2 	Demand and Supply of Labor 
    %   J24 	Human Capital • Skills • Occupational Choice • Labor Productivity 

%   O1 	Economic Development 
    %   O15 	Human Resources • Human Development • Income Distribution • Migration 

%   R2 	Household Analysis  
    % 	R23 	Regional Migration • Regional Labor Markets • Population • Neighborhood Characteristics 





