
%####
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Potential concerns}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



% ========================================
% Some thoughts
% ========================================

\section{Thoughts}

\begin{frame}
    \label{frame:thoughts}
    \frametitle{Thoughts}
    \begin{itemize}
        \item How to think about heterogeneity? We should expect more effects not where there lacks parental suppport but where there is $\rightarrow$ more possibilities of substitution from teachers to parents. But not too much because otherwise they could do it all?
        \item Have school level estimates. Idea was to do heterogeneity. Needed or our excercise is enough?
    \end{itemize}


\end{frame}


\begin{frame}
    \label{frame:research_feedback}
    \frametitle{Threats to identification \textcolor{red}{(for feedback)}}
        Any other thoughts on potential time varying shocks?
        \begin{itemize}
            \item Parent's work
            \item 
            \item There is a shift from private to public enrollment during COVID. If this was more common on siblings... would be composition?
        \end{itemize}

 
    \begin{flushleft}
        \hyperlink{frame:research}{\beamergotobutton{Go Back $\carriagereturn$}}
    \end{flushleft}
    
\end{frame}


\begin{frame}
        \label{frame:Leigh}
    \frametitle{Leigh}
    \begin{itemize}
        \item 
    \end{itemize}
\end{frame}

\begin{frame}
        \label{frame:Scott}
    \frametitle{Scott}
    \begin{itemize}
        \item 
    \end{itemize}
\end{frame}

\begin{frame}
        \label{frame:Rich}
    \frametitle{Rich}
    \begin{itemize}
        \item 
    \end{itemize}
\end{frame}


\begin{frame}
        \label{frame:dean}
    \frametitle{Dean}
    \begin{itemize}
        \item \textbf{Sibsize is not exogenou.}  Sibsize is correlated with parents age (sibsize unfolds over a lifecycle), parents age at first birth, parents employment, parents human capital, housing choices, etc. How much should we really be interpreting this as about sibsize? What if there are two types of parents, those who really care about investing in child quality (H) and human capital and those who do not (L). H types choose to have smaller sibsize so they can invest more in human capital, L types choose quantity over quality. AND when covid comes H types sacrifice more to protect learning than L types do. So you’re not identifying an effect of sibsize; you’re recovering the parents’ endogenous choices that determined sibsize.
    \end{itemize}
\end{frame}

\begin{frame}
        \label{frame:dean2}
    \frametitle{Dean}
    \begin{itemize}
        \item \textbf{Measurement of the dependent variable.}   How is the outcome measured? GPAs seem like they could be directly impacted by covid in ways that are about measurement rather than education. Like, you’re not going to school in the same way, so you’re not being evaluated the same way. I understand that this would be presumably constant by sibship size, but it seems like at a minimum it bears on the interpretation of the results and whether they have a quantitative (rather than just qualitative) interpretation. (It also gets me wondering about strict exogeneity (assuming that you’re using period fixed effects) and the linearity assumptions built into fixed effects.)
    \end{itemize}
\end{frame}

\begin{frame}
        \label{frame:dean3}
    \frametitle{Dean}
    \begin{itemize}
        \item \textbf{Is the effect size quantitatively informative?}   A JMP has to be interesting to get attention. I don’t know that people are going to be super-surprised by the sign of the effect. So is the effect size stably robust, interesting and informative?
    \end{itemize}
\end{frame}

\begin{frame}
        \label{frame:Eric}
    \frametitle{Eric}
    \begin{itemize}
        \item 
    \end{itemize}
\end{frame}

\begin{frame}
        \label{frame:Sandy}
    \frametitle{Sandy}
    \begin{itemize}
        \item 
    \end{itemize}
\end{frame}

\begin{frame}
        \label{frame:Bo}
    \frametitle{Bo}
    \begin{itemize}
        \item 
    \end{itemize}
\end{frame}

\begin{frame}
        \label{frame:Peter}
    \frametitle{Peter}
    \begin{itemize}
        \item 
    \end{itemize}
\end{frame}

\begin{frame}
        \label{frame:Ofer}
    \frametitle{Ofer}
    \begin{itemize}
        \item 
    \end{itemize}
\end{frame}

\begin{frame}
    \label{frame:fabiola}
    \frametitle{Fabiola}
    \begin{itemize}
        \item 
    \end{itemize}
\end{frame}
